### 2019-12-12 docs/paper.tex
add documentation

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2019

% ready for submission
% \usepackage{neurips_2019}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2019}

% to compile a camera-ready version, add the [final] option, e.g.:
     \usepackage[final]{neurips_2019}

% to avoid loading the natbib package, add option nonatbib:
%     \usepackage[nonatbib]{neurips_2019}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Music Classification Using Convolutional Neural Networks}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Submission of papers to NeurIPS 2019}

NeurIPS requires electronic submissions.  The electronic submission site is
\begin{center}
  \url{https://cmt.research.microsoft.com/NeurIPS2019/}
\end{center}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NeurIPS 2019 must be prepared according to the
instructions presented here. Papers may only be up to eight pages long,
including figures. Additional pages \emph{containing only acknowledgments and/or
  cited references} are allowed. Papers that exceed eight pages of content
(ignoring references) will not be reviewed, or in any other way considered for
presentation at the conference.

The margins in 2019 are the same as since 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
  \url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{Preprint option}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2019.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2019+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2019}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
  acceptable for NeurIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All acknowledgments
go at the end of the paper. Do not include acknowledgments in the anonymized
submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references. {\bf Remember that you can use more than eight
  pages as long as the additional pages contain \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2019-12-15 docs/paper.tex
add intro to paper

@@
 
-% if you need to pass options to natbib, use, e.g.:
-%     \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading neurips_2019
-
-% ready for submission
-% \usepackage{neurips_2019}
-
-% to compile a preprint version, e.g., for submission to arXiv, add add the
-% [preprint] option:
-%     \usepackage[preprint]{neurips_2019}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
 \usepackage[final]{neurips_2019}
-
-% to avoid loading the natbib package, add option nonatbib:
-%     \usepackage[nonatbib]{neurips_2019}
-
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to break the
-% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
-% authors names on the first line, and the last on the second line, try using
-% \AND instead of \And before the third author name.
-
 \author{%
-  David S.~Hippocampus\thanks{Use footnote for providing further information
-    about author (webpage, alternative address)---\emph{not} for acknowledging
-    funding agencies.} \\
-  Department of Computer Science\\
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
-  % examples of more authors
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \AND
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
+  Abel Putovici\And
+	Zsombor Molnár
 }
@@
 
-\section{Submission of papers to NeurIPS 2019}
+\section{Introduction}
 
-NeurIPS requires electronic submissions.  The electronic submission site is
-\begin{center}
-  \url{https://cmt.research.microsoft.com/NeurIPS2019/}
-\end{center}
+Music is and has always been one of the most popular forms of art and 
+entertainment. The number of people who use streaming services to consume music 
+has grown to a magnitude of millions in this decade. These services make use of 
+complicated and complex recommender systems to help grow the number of 
+daily active users and to improve their experience of the service. These recommender 
+systems rely on extremely large labeled datasets in order to work properly, and 
+labeling these datasets manually is a very resource-heavy endeavour.
 
-Please read the instructions below carefully and follow them faithfully.
+\subsection{Our Goals}
+
+\paragraph{Music Genres in General}
+
+One possible way of labeling songs is doing it by genre though this introduces 
+other difficulties, since these are ment to indicate the artistic nature of music, an 
+aspect which tends to be highly subjective and controversial. Music genres do not have a 
+proper, formal definition and often overlap as well, making music classification by 
+genre a more difficult task to do right.
+
+\paragraph{Our Primary Goal}
+
+Our primary goal was do deliver a solution which can effectively recognize some of the 
+most popular and generic music genres and assign these as labels to songs of music.
 

### 2019-12-15 docs/paper.tex
add our approach to docs

@@
 
-\subsection{Our Goals}
+\subsection{Our Goal}
 
@@
 most popular and generic music genres and assign these as labels to songs of music.
+
+\section{Our Approach}
+
+There are many existing solutions and research papers regarding the subject and these 
+show absolutely usable methods and results, though each of them tend to have a major 
+drawback: every solution aims to work in \emph{centralized environments} due to their 
+computational requirements. We decided that our approach had to be able to work on 
+edge devices such as smart phones or other, more constrained environments, even on 
+cost of precision. This decision implied a rather small model size and great model 
+simplicity, this is why we chose to try a simple convolutional neural network.
 

### 2019-12-15 docs/paper.tex
add model and results sections

@@
 \usepackage{microtype}      % microtypography
+\usepackage{graphicx}
+\graphicspath{ {./images/} }
 
@@
 
-\subsection{Style}
+\section{The Model}
 
-Papers to be submitted to NeurIPS 2019 must be prepared according to the
-instructions presented here. Papers may only be up to eight pages long,
-including figures. Additional pages \emph{containing only acknowledgments and/or
-  cited references} are allowed. Papers that exceed eight pages of content
-(ignoring references) will not be reviewed, or in any other way considered for
-presentation at the conference.
+\subsection{Trial and Error}
 
-The margins in 2019 are the same as since 2007, which allow for $\sim$$15\%$
-more words in the paper compared to earlier years.
+We went through numerous iterations and tried various convolutional neural 
+network architectures during development. At first we tried to use convolutional 
+windows that would overlap the whole frequency domain and move only in the time domain, 
+since although spectrograms can be regarded as arbitrary two dimensional data, the two 
+axises have different meanings. This path led nowhere, the model was not able to 
+overfit on a small subset of the dataset. We decided to use simple, rectangular convolutional 
+windows, which could be called standard by now. This approach was indeed able to overfit, meaning 
+it was worth to try learning on the whole dataset. Validation error would cease to decrease 
+after the first few epochs. This would be followed by decreasing the input size of the model 
+by splitting the samples of 30 seconds length into 4 smaller fragments.
 
-Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
-NeurIPS website as indicated below. Please make sure you use the current files
-and not previous versions. Tweaking the style files may be grounds for
-rejection.
+\subsection{The Final Model Architecture}
 
-\subsection{Retrieval of style files}
+The final model consists of the following layers:
 
-The style files for NeurIPS and other conference information are available on
-the World Wide Web at
+\begin{itemize}
+\item a convolutional layer with a depth of 32 and a window shape of (2, 6)
+\item another convolutional layer with a depth of 32 and a window shape of (2, 6)
+\item a convolutional layer with a depth of 64 and a window shape identical to the previous ones
+\item a fully connected layer of 512 neurons
+\end{itemize}
+
+Each convolutional layer was followed by a batch normalization 
+layer and a max-pooling layer. L1 and L2 regularizers were adopted to the fully connected layer. 
+The model has an output layer of 10 neurons with \emph{softmax} as activation function.
+
+\subsection{Hyperparameters}
+\paragraph{Activation functions}
+At first we tried using \emph{ReLU} activations between each layer. This lead to many issues, 
+since in the context of Mel spectrograms negative numbers have significance. Perceiving this, 
+we decided to use \emph{Hyperbolic Tangent} as activation function.
+
+\paragraph{Loss Function}
+The loss function used is \emph{Sparse Categorical Crossentropy} since the labels are not one-hot encoded.
+
+\paragraph{Optimizer}
+The optimizer algorithm used during training was Stochastic Gradient Descent with a learning rate of 0.01. 
+At first we've tried with \emph{Adam} but it did not perform quite as expected. The next choice 
+was \emph{Adadelta} which showed promising results, but it did not appear to stable due to the 
+fluctuation we have observed on both the graphs of training and validation accuracy.
+
+\paragraph{Number of Epoch and Data Split}
+The model was trained for 100 epochs with a batch size of 5. 80 percent of the data was used 
+for training, 10 percent was used for validation and the last 10 percent was used for testing.
+
+\paragraph{Vanishing Gradient}
+
+During the training process we've noticed that after a certain number of epochs 
+the validation accuracy would cease to converge. This was due to the Vanishing 
+Gradient problem, which led to the choice of using \emph{Linear} activation between the 
+convolutional layers, leaving \emph{Hyperbolic Tangent} only between the output and 
+the fully connected layer.
+
+\section{Results}
+
+\subsection{Training and Validation}
+
+The model is still overfitting with the validation accuracy being stuck at \~60\% and the training accuracy soaring.
+
 \begin{center}
-  \url{http://www.neurips.cc/}
+    \includegraphics[scale=0.5]{acc}
+		\includegraphics[scale=0.5]{loss}
 \end{center}
-The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the
-various formatting requirements your NeurIPS paper must satisfy.
 
-The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
-  Microsoft Word, and RTF are no longer supported!}
+\subsection{Testing Accuracy}
 
-The \LaTeX{} style file contains three optional arguments: \verb+final+, which
-creates a camera-ready copy, \verb+preprint+, which creates a preprint for
-submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
-\verb+natbib+ package for you in case of package clash.
+The final testing accuracy of the model is \textbf{0.61\%}. Below are the Classication Matrix and the final 
+Classification Report.
 
-\paragraph{Preprint option}
-If you wish to post a preprint of your work online, e.g., on arXiv, using the
-NeurIPS style, please use the \verb+preprint+ option. This will create a
-nonanonymized version of your work with the text ``Preprint. Work in progress.''
-in the footer. This version may be distributed as you see fit. Please \textbf{do
-  not} use the \verb+final+ option, which should \textbf{only} be used for
-papers accepted to NeurIPS.
-
-At submission time, please omit the \verb+final+ and \verb+preprint+
-options. This will anonymize your submission and add line numbers to aid
-review. Please do \emph{not} refer to these line numbers in your paper as they
-will be removed during generation of camera-ready copies.
-
-The file \verb+neurips_2019.tex+ may be used as a ``shell'' for writing your
-paper. All you have to do is replace the author, title, abstract, and text of
-the paper with your own.
-
-The formatting instructions contained in these style files are summarized in
-Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
-type with a vertical spacing (leading) of 11~points.  Times New Roman is the
-preferred typeface throughout, and will be selected for you by default.
-Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
-indentation.
-
-The paper title should be 17~point, initial caps/lower case, bold, centered
-between two horizontal rules. The top rule should be 4~points thick and the
-bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
-below the title to rules. All pages should start at 1~inch (6~picas) from the
-top of the page.
-
-For the final version, authors' names are set in boldface, and each name is
-centered above the corresponding address. The lead author's name is to be listed
-first (left-most), and the co-authors' names (if different address) are set to
-follow. If there is only one co-author, list both author and co-author side by
-side.
-
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-All headings should be lower case (except for first word and proper nouns),
-flush left, and bold.
-
-First-level headings should be in 12-point type.
-
-\subsection{Headings: second level}
-
-Second-level headings should be in 10-point type.
-
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the heading in
-bold, flush left, and inline with the text, with the heading followed by 1\,em
-of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.  Citations may be
-author/year or numeric, as long as you maintain internal consistency.  As to the
-format of the references themselves, any style is acceptable as long as it is
-used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations appropriate for
-use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may add the
-following before loading the \verb+neurips_2019+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add the optional
-argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{neurips_2019}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the third
-person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
-previous work [4].'' If you cite your other papers that are not widely available
-(e.g., a journal paper under review), use anonymous author names in the
-citation, e.g., an author of the form ``A.\ Anonymous.''
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote, indicate
-footnotes with a number\footnote{Sample of the first footnote.} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-\begin{figure}
+\begin{table}[h]
+  \caption{Confusion Matrix}
   \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-All artwork must be neat, clean, and legible. Lines should be dark enough for
-purposes of reproduction. The figure number and caption always appear after the
-figure. Place one line space before the figure caption and one line space after
-the figure. The figure caption should be lower case (except for first word and
-proper nouns); figures are numbered consecutively.
-
-You may use color figures.  However, it is best for the figure captions and the
-paper body to be legible if the paper is printed in either black/white or in
-color.
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table number and
-title always appear before the table.  See Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical rules.} We
-strongly suggest the use of the \verb+booktabs+ package, which allows for
-typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule(r){1-2}
-    Name     & Description     & Size ($\mu$m) \\
+  \begin{tabular}{l | llllllllll}
+    Genre & Metal & Classical & Reggae & Jazz & Country & Rock & Hiphop & Disco & Pop & Blues \\
     \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
+    Metal & 44 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		Classical & 0 & 28 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 \\
+		Reggae & 1 & 1 & 18 & 0 & 1 & 2 & 5 & 3 & 8 & 5 \\
+    Jazz & 1 & 11 & 0 & 28 & 1 & 1 & 0 & 0 & 1 & 2 \\
+		Country & 0 & 2 & 0 & 3 & 20 & 1 & 0 & 0 & 0 & 4 \\
+		Rock & 12 & 0 & 0 & 2 & 5 & 16 & 4 & 2 & 1 & 4 \\
+		Hiphop & 7 & 0 & 1 & 0 & 0 & 0 & 28 & 0 & 1 & 2 \\
+		Disco & 4 & 1 & 4 & 0 & 1 & 9 & 7 & 8 & 7 & 2 \\
+		Pop & 0 & 3 & 1 & 0 & 3 & 2 & 2 & 0 & 35 & 2 \\
+		Blues & 1 & 1 & 0 & 5 & 2 & 0 & 0 & 1 & 0 & 20 \\
     \bottomrule
@@
 
-\section{Final instructions}
+\begin{table}[h]
+  \caption{Classification Report}
+  \centering
+  \begin{tabular}{l | l l l l}
+    Genre & Precision & Recall & F1-Score & Support (number of samples) \\
+    \midrule
+       metal   &    1.00   &   0.63  &    0.77    &    70 \\
+   classical    &   0.93    &  0.60  &    0.73    &    47 \\
+      reggae    &   0.41    &  0.75   &   0.53    &    24 \\
+        jazz    &   0.63    &  0.74   &   0.68    &    39 \\
+     country    &   0.67    &  0.59   &   0.62    &    34 \\
+        rock    &   0.35    &  0.50   &   0.41    &    32 \\
+      hiphop    &   0.72    &  0.61   &   0.66    &    46 \\
+       disco    &   0.19    &  0.57   &   0.28    &    14 \\
+         pop    &   0.73    &  0.66   &   0.69    &    53 \\
+       blues    &   0.67   &   0.49   &   0.56   &     41 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
-Do not change any aspects of the formatting parameters in the style files.  In
-particular, do not modify the width or length of the rectangle the text should
-fit into, and do not change font sizes (except perhaps in the
-\textbf{References} section; see below). Please note that pages should be
-numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and not, for
-example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file must only
-contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
-achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
-  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
-  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
-  available out-of-the-box on most Linux machines.
-
-\item The IEEE has recommendations for generating PDF files whose fonts are also
-  acceptable for NeurIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
-  "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
-  the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
-for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
-workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
-you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
-figure width as a multiple of the line width as in the example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
-necessary.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All acknowledgments
-go at the end of the paper. Do not include acknowledgments in the anonymized
-submission, only in the final paper.
+\begin{table}[h]
+  \caption{Classification Report Averages}
+  \centering
+  \begin{tabular}{l | l l l l}
+    Type & Precision & Recall & F1-Score & Support (number of samples) \\
+    \midrule
+		Macro Average & 0.63 & 0.61 & 0.59 & 400 \\
+		Weighted Average & 0.71 & 0.61 & 0.64 & 400 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2019-12-15 docs/paper.tex
add future improvements
merge

@@
     simplicity, this is why we chose to try a simple convolutional neural network.
+
+	\section{The dataset}
+
+	We wanted to have a great vatiety of song samples in large quantity.
+	The first dataset we took into account is the \textit{Million Song Dataset} \cite{million}.
+	The sheer number of samples was quite promissing, but it turned out to be overwhelming.
+	Not to mention the fact that it contained numerous pieces of information that we did not need, like the authors,
+	the release year and other different identifiers for database use. 
+	It needed a lot of time just to extract the necessary information we need, which would make the extension 
+	of the used dataset unnecessarily time consuming.
+
+	Our second option was the GTZAN \cite{gtzan_art} dataset used in the \textit{Musical genre classification of audio signals} \cite{gtzan}.
+	It suited our needs and it covered samples from 10 clearly distinct music genres, 100 tracks each.
+	As for the length of the songs, the dataset contained 30 second long samples from different parts of the songs.
+	An analysis done by Bob L. Strum \cite{gtzan_anal} describes more precisely the capacity of this dataset.
 
@@
 
+    \section{Future Improvements}
+
+    There are many ways the solution could be improved. Our plans include
+
+    \begin{itemize}
+        \item augmenting the dataset by time-stretching (and squeezing) and splitting the 30 second
+        samples using slightly overlapping windows
+        \item experimenting with different network architectures
+        \item applying \emph{Hyperparameter Optimization}
+        \item maybe searching for network architectures using experimental solutions like \emph{AutoML}
+    \end{itemize}
+
     \section*{References}

### 2019-12-15 docs/paper.tex
add abstract

@@
 \begin{abstract}
-        The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
-        both the left- and right-hand margins. Use 10~point type, with a vertical
-        spacing (leading) of 11~points. The word \textbf{Abstract} must be centered,
-        bold, and in point size 12. Two line spaces precede the abstract. The abstract
-        must be limited to one paragraph.
+	In this paper we describe a convolutional neural network designed to classify music by genre.
+	The base idea came from an article we read about the combination of CNN and mathematical algorithms for a music classification \cite{sample}.
+	At the moment the network can categorise at a 61\% accuracy.
+	We use the GTZAN dataset with slight modifications as it covers all our needs.
+	During the building of this network we encountered numerous challenges, especially with the activation functions.
+	A constant problem was overlearning, which we could only delay. 
 \end{abstract}

### 2019-12-15 docs/paper.tex
add fix
Create references to bibliography

@@
 
-    The final testing accuracy of the model is \textbf{0.61\%}. Below are the Classication Matrix and the final
+    The final testing accuracy of the model is \textbf{61\%}. Below are the Classication Matrix and the final
     Classification Report.
@@
 
-    \section*{References}
-
-    References follow the acknowledgments. Use unnumbered first-level heading for
-    the references. Any choice of citation style is acceptable as long as you are
-    consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-    when listing the references. {\bf Remember that you can use more than eight
-    pages as long as the additional pages contain \emph{only} cited references.}
-    \medskip
-
-    \small
-
-    [1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
-    connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
-    (eds.), {\it Advances in Neural Information Processing Systems 7},
-    pp.\ 609--616. Cambridge, MA: MIT Press.
-
-    [2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
-    Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
-    TELOS/Springer--Verlag.
-
-    [3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
-    recall at excitatory recurrent synapses and cholinergic modulation in rat
-    hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
+    \bibliographystyle{plain}
+    \bibliography{bibs}
 

### 2019-12-15 docs/paper.tex
Correct grammar errors

@@
 	In this paper we describe a convolutional neural network designed to classify music by genre.
-	The base idea came from an article we read about the combination of CNN and mathematical algorithms for a music classification \cite{sample}.
+	The base idea came from an article we read about the combination of CNN and mathematical algorithms for music classification \cite{sample}.
 	At the moment the network can categorise at a 61\% accuracy.
 	We use the GTZAN dataset with slight modifications as it covers all our needs.
-	During the building of this network we encountered numerous challenges, especially with the activation functions.
+	During the building of this neural network we encountered numerous challenges, especially with the activation functions.
 	A constant problem was overlearning, which we could only delay. 
@@
     since although spectrograms can be regarded as arbitrary two dimensional data, the two
-    axises have different meanings. This path led nowhere, the model was not able to
+    axises have different meanings. This path led nowhere, as the model was not able to
     overfit on a small subset of the dataset. We decided to use simple, rectangular convolutional
@@
     At first we've tried with \emph{Adam} but it did not perform quite as expected. The next choice
-    was \emph{Adadelta} which showed promising results, but it did not appear to stable due to the
+    was \emph{Adadelta} which showed promising results, but it did not appear to stabilize due to the
     fluctuation we have observed on both the graphs of training and validation accuracy.
